Concurrent Programming with CXL

### 2020-06-23 book/paper.tex
Latest

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/UpEnter.cxl}
\end{code}
\caption{[UpEnter.py] Broken attempt at fixing the code of Figure~\ref{fig:inc}.}
\label{fig:incenter}
\end{figure}

@@

A method \texttt{m} with argument \texttt{a} is invoked in its
most basic form as follows (assigning the result to \texttt{r}).
\begin{code}
\begin{verbatim}
r = m a;
\end{verbatim}
\end{code}
That's right, no parentheses are required.  In fact, if you invoke
\texttt{m(a)}, the argument is \texttt{(a)}, which is the same
as \texttt{a}.
If you invoke \texttt{m()}, the argument is \texttt{()},
which is the empty tuple.
If you invoke \texttt{m(a, b)}, the argument is \texttt{(a, b)},
the tuple consisting of values \texttt{a} and \texttt{b}.

@@

Figure~\ref{fig:barrierdiagram} shows a high-level depiction with three
processes.  Initially all processes are in round 0.  Then each process
can start and finish the round.  However, none of the processes can
progress to the next round until all processes have finished the
current round.

@@

\begin{quote}
\begin{itemize}
\item See if you can implement barrier synchronization for $N$ processes
with just three semaphores.  Busy waiting is not allowed.
\item How about just two?
\end{itemize}
\end{quote}

>>>>

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/UpEnter.cxl}
\end{code}
\caption{[UpEnter.cxl] Broken attempt at fixing the code of Figure~\ref{fig:inc}.}
\label{fig:incenter}
\end{figure}

@@

A method \texttt{m} with argument \texttt{a} is invoked in its
most basic form as follows (assigning the result to~\texttt{r}).
\begin{code}
\begin{verbatim}
r = m a;
\end{verbatim}
\end{code}
That's right, no parentheses are required.  In fact, if you invoke
\texttt{m(a)}, the argument is \texttt{(a)}, which is the same
as \texttt{a}.
If you invoke \texttt{m()}, the argument is \texttt{()},
which is the empty tuple.
If you invoke \texttt{m(a, b)}, the argument is \texttt{(a, b)},
the tuple consisting of values \texttt{a} and \texttt{b}.

@@

Figure~\ref{fig:barrierdiagram} shows a high-level depiction with three
processes.  Initially all processes are in round~0.  Then each process
can start and finish the round.  However, none of the processes can
progress to the next round until all processes have finished the
current round.

@@

\section*{Exercises}
\begin{problems}
\item See if you can implement barrier synchronization for $N$ processes
with just three semaphores.  Busy waiting is not allowed.  How about just two?
\end{problems}
